\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-27 doc/sui14/relatedwork.tex
relatedwork: add one more citation

\subsection{Vision- and Projection-Based Target Selection}
\changes{Many alternative solutions for detecting devices in contained spaces
rely on computer-vision recognition of printed tags on devices. Unfortunately, these methods either impose significant constraints
on the camera used for detection~\cite{Bokode}, require large, obtrusive tags, or are
designed to work specifically at short distances~\cite{CyberCode}. Passive markers also cannot show visual feedback in the environment. 
Handheld projectors can both display a user interface in space and communicate control information optically, e.g., by encoding information temporally (using Gray codes in Picontrol~\cite{schmidt_picontrol:_2012} and RFIG Lamps~\cite{raskar_rfig_2004}) or spatially (using QR codes in the infrared spectrum in SideBySide~\cite{willis_sidebyside:_2011}). Our solution is similar in spirit but relies on simple low-cost IR emitters and detectors. \bjoern{need a stronger statement here}}

>>>>

\subsection{Vision- and Projection-Based Target Selection}
\changes{Many alternative solutions for detecting devices in contained spaces
rely on computer-vision recognition of printed tags on devices. Unfortunately,
these methods either impose significant constraints on the camera used for
detection~\cite{Bokode}, require large or obtrusive tags~\cite{Dataglyphs}, or
are designed to work specifically at short distances~\cite{CyberCode}. Passive
markers also cannot show visual feedback in the environment.  Handheld
projectors can both display a user interface in space and communicate control
information optically, e.g., by encoding information temporally (using Gray
codes in Picontrol~\cite{schmidt_picontrol:_2012} and RFIG
Lamps~\cite{raskar_rfig_2004}) or spatially (using QR codes in the infrared
spectrum in SideBySide~\cite{willis_sidebyside:_2011}). Our solution is similar
in spirit but relies on simple low-cost IR emitters and detectors. \bjoern{need
a stronger statement here}}
